\topskip0pt
\vspace*{\fill}
\begin{center}
    \huge{\textsc{Acknowledgments}}
    \end{center}
    
    I would like to acknowledge the help of some people who were crucial for the completion of this thesis.
    
    First I would like to thank my two supervisors: Prof. Jean-Didier Legat and Prof. Christophe de Vleeschouwer for their support. They provided valuable advice helping me to define the scope of this work and guiding mee through its completion.
    
    Second, I would like to thank the two readers of this thesis: Martin Lefevre and Victor Joos de ter Beerst for devoting their time to read this thesis and asssess my work
    
    Third, I wish to acknowledge the assistance provided by Victor Joos de ter Beerst and Antoine Vanderschueren to accomplish this work which was valuable for me. Their availability to answer my questions was a great help.
    
    Fourth, I would like to thank my family and friends, who were always there to help me when I needed the most. I want also to acknowledge the support of Clara, who was a huge source of inspiration to outdo myself. Moreover, special thanks go to the members of the IngiGang for the time spent during those five years together and the support They provided me.
    
    Finally, I would like to personnally thank all the people who have proofread this thesis, in particular Martine, Julie, Florian, Martin, Maxime, and last but not least Guillaume for giving their precious time to improve the quality of this work. 
\vspace*{\fill}
\afterpage{\blankpage}
\newpage
